---
title: "Results"
---

<!-- ═══════════════════════════════════════════════════════════════
     03-results.qmd — RESULTS
     
     SOURCE ASSIGNMENTS TO DRAW FROM:
       • Data Wrangling [R] (Week 13) — coding_data_clean.RDS
       • Describing Data [R] (Week 14) — frequency table + bar chart
       • Inferencing Data [R] (Week 15) — Chi-Square test
     
     ✏️  WHAT TO DO HERE:
       1. Drop your coding_data_clean.RDS file into the project
          folder (same level as this file).
       2. In EACH code chunk, replace the placeholder variable
          names (var1, var2, etc.) with YOUR actual column names.
       3. Update the figure captions and narrative text to reflect
          your actual findings.
       4. The code is set to echo: false globally, so only outputs
          (tables, charts) appear in the rendered document.
          Set echo: true on any chunk if you want to show the code.
       5. Delete all instruction comments before rendering.
     ═══════════════════════════════════════════════════════════════ -->

::: {.section-badge}
Phase IV · The Analyst
:::

```{r}
#| label: setup
#| include: false

# ── Load packages ──────────────────────────────────────────────────
# If any package is missing, run: install.packages("PACKAGE_NAME")
library(tidyverse)
library(knitr)
library(kableExtra)

# ── Load your cleaned data ─────────────────────────────────────────
# Make sure coding_data_clean.RDS is in the project folder.
# If it is in a subfolder, adjust the path: "data/coding_data_clean.RDS"
coding_data <- readRDS("reddit_ai_video_games_coded.rds")

# ── Quick sanity check (visible only when you run interactively) ───
# glimpse(coding_data)
# summary(coding_data)
```

This section presents the findings of the content analysis (N = `r nrow(coding_data)` items). Results are organized to address each research question in turn. Descriptive statistics are presented first, followed by inferential analysis.

---

## Descriptive Statistics

### Overview of the Sample

```{r}
#| label: tbl-sample-overview
#| tbl-cap: "Table 1. Sample composition by [VARIABLE — e.g., outlet, year, or another grouping variable]."

# ── INSTRUCTIONS ───────────────────────────────────────────────────
# Replace `outlet` with your actual grouping/administrative variable.
# This table gives readers a sense of where your data came from.
# ──────────────────────────────────────────────────────────────────

coding_data |>
  count(outlet, name = "outlet") |>                    # ← replace `outlet`
  mutate(
    Percent = round(n / sum(n) * 100, 1),
    Percent = paste0(Percent, "%")
  ) |>
  rename(
    "Source / Outlet" = outlet,                   # ← replace `outlet`
    "n" = n,
    "% of Sample" = Percent
  ) |>
  kable(align = c("l", "c", "c")) |>
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = TRUE,
    font_size = 13
  ) |>
  row_spec(0, bold = TRUE, background = "#b71c1c", color = "white")
```

*(2–3 sentences describing Table 1. For example: "The sample was drawn from [N sources/outlets]. The largest share of items came from [SOURCE], accounting for X% of the total sample. Coverage was distributed [evenly/unevenly] across the study period.")*

---

### Distribution of Primary Variable: [Variable 1 Name]

```{r}
#| label: tbl-var1-freq
#| tbl-cap: "Table 2. Frequency distribution of [Variable 1 Name] (N = XX, excluding code-9 items)."

# ── INSTRUCTIONS ───────────────────────────────────────────────────
# Replace `var1` with your first primary variable column name.
# Replace "Unable to Determine" with whatever your code-9 label is.
# ──────────────────────────────────────────────────────────────────

coding_data |>
  filter(var1 != "Unable to Determine") |>        # ← replace `var1`
  count(var1, name = "n") |>                      # ← replace `var1`
  arrange(desc(n)) |>
  mutate(
    Percent = round(n / sum(n) * 100, 1),
    `Cumulative %` = round(cumsum(Percent), 1),
    Percent = paste0(Percent, "%"),
    `Cumulative %` = paste0(`Cumulative %`, "%")
  ) |>
  rename(
    "[Variable 1 Name]" = var1,                   # ← replace both
    "N" = n
  ) |>
  kable(align = c("l", "c", "c", "c")) |>
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = TRUE,
    font_size = 13
  ) |>
  row_spec(0, bold = TRUE, background = "#b71c1c", color = "white")
```

*(2–3 sentences describing Table 2. Report the most and least common categories. Connect to RQ1: does this distribution speak to what your first research question was asking?)*

---

### Bar Chart: Distribution of [Variable 1 Name]

```{r}
#| label: fig-var1-bar
#| fig-cap: "Figure 1. Distribution of [Variable 1 Name] across all coded items (N = XX, code-9 excluded). [Add 1 sentence describing the most important visual pattern here — captions should be self-contained.]"
#| fig-width: 7
#| fig-height: 4.5

# ── INSTRUCTIONS ───────────────────────────────────────────────────
# Replace `var1` with your variable column name.
# Adjust the fill color, axis labels, and title to match your study.
# The theme_minimal() + custom colors keep it professional.
# ──────────────────────────────────────────────────────────────────

coding_data |>
  filter(var1 != "Unable to Determine") |>        # ← replace `var1`
  count(var1) |>                                  # ← replace `var1`
  mutate(
    pct = n / sum(n),
    var1 = fct_reorder(var1, n, .desc = TRUE)     # ← replace `var1` (×2)
  ) |>
  ggplot(aes(x = var1, y = pct, fill = var1)) +  # ← replace `var1` (×2)
  geom_col(width = 0.65, show.legend = FALSE) +
  geom_text(
    aes(label = paste0(round(pct * 100, 1), "%")),
    vjust = -0.4,
    size = 3.5,
    color = "#333333"
  ) +
  scale_y_continuous(
    labels = scales::percent_format(accuracy = 1),
    limits = c(0, 1),
    expand = expansion(mult = c(0, 0.08))
  ) +
  scale_fill_manual(values = c(
    "#b71c1c", "#e57373", "#ef9a9a", "#ffcdd2", "#880e4f"
    # Add or remove colors to match the number of categories you have
  )) +
  labs(
    title = "Distribution of [Variable 1 Name]",
    subtitle = "Source: [YOUR ARCHIVE], [DATE RANGE] | N = XX",
    x = "[Variable 1 Name]",
    y = "Proportion of Items"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(face = "bold", color = "#b71c1c"),
    plot.subtitle = element_text(color = "#666666", size = 9),
    axis.title = element_text(color = "#333333"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  )
```

*(2–3 sentences interpreting Figure 1. What is the dominant category? How concentrated or spread is the distribution? Does anything stand out as unexpected?)*

---

### Distribution of Secondary Variable: [Variable 2 Name]

```{r}
#| label: tbl-var2-freq
#| tbl-cap: "Table 3. Frequency distribution of [Variable 2 Name] (N = XX, excluding code-9 items)."

coding_data |>
  filter(var2 != "Unable to Determine") |>        # ← replace `var2`
  count(var2, name = "n") |>                      # ← replace `var2`
  arrange(desc(n)) |>
  mutate(
    Percent = round(n / sum(n) * 100, 1),
    Percent = paste0(Percent, "%")
  ) |>
  rename(
    "[Variable 2 Name]" = var2,                   # ← replace both
    "N" = n
  ) |>
  kable(align = c("l", "c", "c")) |>
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = TRUE,
    font_size = 13
  ) |>
  row_spec(0, bold = TRUE, background = "#b71c1c", color = "white")
```

*(2–3 sentences describing Table 3. Which category was most common? Least common? Does this align with what you expected based on your qualitative memo?)*

---

## Inferential Analysis

### Chi-Square Test of Independence: [Variable 1] × [Variable 2]

<!-- ── SECTION PURPOSE ─────────────────────────────────────────────
     The Chi-Square test asks: Is there a statistically significant
     relationship between Variable 1 and Variable 2?
     
     Before running, make sure:
       • Both variables are factors (categorical)
       • You have excluded code-9 rows
       • Each expected cell count is ≥ 5 (check output of test)
     
     If expected cell counts are too low, consider collapsing
     categories (e.g., merging 2 low-frequency categories into
     an "Other" category) and note this in your text.
     ──────────────────────────────────────────────────────────────── -->

```{r}
#| label: tbl-crosstab
#| tbl-cap: "Table 4. Cross-tabulation of [Variable 1 Name] by [Variable 2 Name] (N = XX, code-9 excluded)."

# ── INSTRUCTIONS ───────────────────────────────────────────────────
# Replace `var1` and `var2` with your actual variable column names.
# ──────────────────────────────────────────────────────────────────

# Filter out code-9 rows for both variables
chi_data <- coding_data |>
  filter(
    var1 != "Unable to Determine",               # ← replace `var1`
    var2 != "Unable to Determine"                # ← replace `var2`
  )

# Cross-tabulation table
cross_tab <- table(chi_data$var1, chi_data$var2)  # ← replace both

# Display as formatted table
cross_tab |>
  as.data.frame.matrix() |>
  rownames_to_column(var = "[Variable 1 Name]") |>  # ← replace label
  kable(align = "lcccc") |>
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = TRUE,
    font_size = 13
  ) |>
  add_header_above(
    c(" " = 1, "[Variable 2 Name]" = ncol(cross_tab))  # ← replace label
  ) |>
  row_spec(0, bold = TRUE, background = "#b71c1c", color = "white")
```

*(2–3 sentences describing Table 4 — the cross-tab. Which cell combinations were most common? Were any cells surprisingly empty or surprisingly full?)*

```{r}
#| label: chi-square-test
#| include: false

# ── Run the Chi-Square test ────────────────────────────────────────
chi_result <- chisq.test(cross_tab)

# ── Extract values for inline reporting ───────────────────────────
chi_x2  <- round(chi_result$statistic, 2)
chi_df  <- chi_result$parameter
chi_p   <- round(chi_result$p.value, 3)
chi_sig <- ifelse(chi_result$p.value < .05, "statistically significant", "not statistically significant")

# ── Check expected cell counts ────────────────────────────────────
# Any expected count below 5 is a concern. Check: chi_result$expected
min_expected <- round(min(chi_result$expected), 2)
```

**Chi-Square Result:**

A Chi-Square test of independence was conducted to examine the relationship between [Variable 1 Name] and [Variable 2 Name]. The result was `r chi_sig`, χ²(`r chi_df`) = `r chi_x2`, *p* = `r chi_p`.

```{r}
#| label: fig-mosaic
#| fig-cap: "Figure 2. Mosaic plot showing the relationship between [Variable 1 Name] and [Variable 2 Name]. Cell width represents the proportion of items in each [Variable 2] category; cell height represents the proportion assigned each [Variable 1] value."
#| fig-width: 7
#| fig-height: 5

# ── INSTRUCTIONS ───────────────────────────────────────────────────
# A mosaic plot visualizes the Chi-Square relationship.
# Replace `var1` and `var2` with your actual column names.
# Replace axis labels with your variable names.
# ──────────────────────────────────────────────────────────────────

chi_data |>
  count(var2, var1) |>                           # ← replace both
  group_by(var2) |>                              # ← replace `var2`
  mutate(prop = n / sum(n)) |>
  ggplot(aes(x = var2, y = prop, fill = var1)) + # ← replace both
  geom_col(position = "fill", width = 0.7, color = "white", linewidth = 0.4) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_manual(values = c(
    "#b71c1c", "#e57373", "#ef9a9a", "#ffcdd2", "#880e4f"
  )) +
  labs(
    title = "[Variable 1 Name] by [Variable 2 Name]",
    subtitle = paste0(
      "χ²(", chi_df, ") = ", chi_x2, ", p = ", chi_p,
      " | Source: [YOUR ARCHIVE], [DATE RANGE]"
    ),
    x = "[Variable 2 Name]",
    y = "Proportion",
    fill = "[Variable 1 Name]"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(face = "bold", color = "#b71c1c"),
    plot.subtitle = element_text(color = "#666666", size = 9),
    axis.text.x = element_text(angle = 25, hjust = 1),
    legend.position = "right"
  )
```

*(3–5 sentences interpreting the Chi-Square result in plain English. Required elements:*
*① State whether the result is significant at α = .05.*
*② If significant: describe the direction of the relationship — which combination of categories was more or less common than expected? Reference Figure 2.*
*③ If not significant: state clearly that the data did not provide evidence of a relationship between the two variables, and note what this means for your RQ2.*
*④ Report the minimum expected cell count (`r min_expected`) and note whether it meets the ≥ 5 assumption.)*

---

## Summary of Findings

<!-- ── SECTION PURPOSE ─────────────────────────────────────────────
     A brief bulleted or short-paragraph summary of ALL key results
     before the reader moves to Discussion. Think of this as a
     "results at a glance" for the website reader.
     ──────────────────────────────────────────────────────────────── -->

::: {.callout-note}
## Key Findings at a Glance

- **RQ1** ([PASTE RQ1 SHORT FORM]): [1-sentence summary of the descriptive finding that addresses RQ1 — e.g., "The most common tone in coverage was Negative (X%), followed by Neutral (X%) and Positive (X%)."]

- **RQ2** ([PASTE RQ2 SHORT FORM]): [1-sentence summary of the inferential finding — e.g., "A statistically significant relationship was found between tone and source type, χ²(X) = X.XX, p = .XXX, suggesting that [DIRECTION OF RELATIONSHIP]."]
:::
